Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-11-02 02_Paper/paper.tex
classifier update.

\subsection{Classifier optimization and testing}
We work with a total of 462 measurements. 
\begin{table}
       \begin{tabular}{ c c }
              Support Vector Machine & 95.\% \\
              Multilinear Perceptron & 95.\% \\
              Random Forest          & 100\%
       \end{tabular}
       \caption{Method comparison for fault detection using the industry demo data test set.}
\end{table}

>>>>

\subsection{Classifier optimization and testing}
We work with a total of 132 measurements. Each containing arm and belt data
logs of individual cell runs. 20 samples are set aside at random for testing 
purposes, leaving 112 training samples. The random seed is set to 1

We compare a total of three different classifier architectures on the data.
A Support Vector Machine (SVM), a multilinear perceptron and a Random Forest
structure. 
\begin{table}
       \begin{tabular}{ c c }
              Support Vector Machine & 95.\% \\
              Multilinear Perceptron & 95.\% \\
              Random Forest          & 100\%
       \end{tabular}
       \caption{Method comparison for fault detection using the industry demo data test set.}
       \label{tab:class_comp}
\end{table}
Results are shown in table~\ref{tab:class_comp}. For 55 of the total 132 samples
quality measurements indicate a problem. This sets the 
baseline over the entire data set, that would be obtained by simply labeling all samples
as good. Over the entire data set, we require to classify more than 58.3\% of the data correctly.
The test set contains eight incorrect samples. We would therefore expect the naive classifier
to produce a 60\% accuracy, which we have to beat. In Table~\ref{tab:class_comp},
we observe that this is indeed the case for all three approaches evaluated here.
